Response to the defense feedback

### 2021-05-30 Chapter-5/Chapter-5.tex
Updates from Overleaf

\subsection{Channel Capacity}
Let $k$ be one of the possible
value of $K$. The Shannon entropy $H(K)$ is defined as
\begin{equation}\label{chapter5:eq1}
  H(K) = - \sum_{k {\in} K}p(k)\log_2(k)
\end{equation}

Shannon entropy can be used to quantify the initial uncertainty about the sensitive information. It measures the amount of information in a system. For example, an AES encryption program takes a 128-bit key as the input. Suppose each key has the equal opportunity and $p_k = 1/ 2^{128}$, then the encryption system has $128 \, \mathit{bits}$ information according to Shannon entropy.

In the chapter, we use the channel capacity to describe the amount of information leakages through a channel. In information theory, the channel capacity is used to quantify the rate of information can be reliably transmitted over a channel. If we use $K$ to represent the input secrets and $O$ to represent the output observation. The channel capacity ($C$) is defined as

>>>>

\subsection{Channel Capacity}
$K$ is a random variable.
Let $k$ be one of the possible
values of $K$. The Shannon entropy $H(K)$ is defined as
\begin{equation}\label{chapter5:eq1}
  H(K) = - \sum_{k {\in} K}p(k)\log_2(k)
\end{equation}

Shannon entropy can be used to quantify the initial uncertainty about sensitive information. It measures the amount of information in a system. For example, an AES encryption program takes a 128-bit key as the input. Suppose each key has the equal opportunity and $p_k = 1/ 2^{128}$, then the encryption system has $128 \, \mathit{bits}$ information according to Shannon entropy.

In this chapter, we use the channel capacity to describe the amount of information leakages through a channel. In information theory, the channel capacity is used to quantify the rate of information can be reliably transmitted over a channel. If we use $K$ to represent the input secrets and $O$ to represent the output observation. The channel capacity ($C$) is defined as
